Methods for Large Scale Learning to Rank

### 2014-09-24 report/Chapters/Introduction.tex
bbeter

The appearance of benchmark data sets gave insight in the performance of different Learning to Rank approaches, which resulted in increasing popularity of those methods that showed to perform well on one or more benchmark data sets. Up to now it remains unknown whether popular existing Learning to Rank methods scale well when they are used in a parallel manner using the MapReduce framework. This thesis aims to be an exploratory start in this little researched area of parallel Learning to Rank. A more extensive overview of my research goals and questions are described in section \ref{sec:goals}.\\

>>>>

The appearance of benchmark data sets gave insight in the performance of different Learning to Rank approaches, which resulted in increasing popularity of those methods that showed to perform well on one or more benchmark data sets. Up to now it remains unknown whether popular existing Learning to Rank methods scale well when they are used in a parallel manner using the MapReduce framework. This thesis aims to be an exploratory start in this little researched area of parallel Learning to Rank.\\
